A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-05-12 bioc-workflow.Rmd
QC section

```{r makeMSnSet, echo=FALSE, message=FALSE, warning=FALSE}
library("MSnbase")

@@

>>>>

```{r makeMSnSet, message=FALSE, warning=FALSE}
library("MSnbase")

@@

Data quality is routinely examined through visualisation to verify that sub-cellular niches have been separated along the gradient. Based on De Duve's principle [@DeDuve:1981] proteins that co-localise exhibit similar quantitation profiles across the gradient fractions employed. One approach that has been widely used to visualise and inspect highthrouput mass spectrometry-based proteomics data is principal components analysis (PCA). PCA is one of many dimensionality reduction methods, that allow one to effectively summarise multi-dimensional data in to 2 or 3 dimensions to enable visualisation. Very generally, the original continuous multi-dimensional data is transformed into a set of orthogonal components ordered according to the amount of variability that they describe. The `plot2D` method in `pRoloc` allows one to plot the principal components (PCs) of a dataset against one another, by default the first two components are plotted on the `x`- and `y`-axis, respectively (the `dims` argument can be used to plot other PCs). If distinct clusters are observed, we assume that there is organellar separation present in the data. In the code chunk below we produce a PCA plot of the mouse stem cell dataset. One point on the plot represents one protein. We can indeed see many distinct protein clusters. Although, plotting the PCs does not give us a hard quantitative measure of separation, it is extremely useful summarising complex experimental information in one figure, to get an overview of the data.

```{r qcplot, message=FALSE, warning=FALSE}
library('pRoloc')
plot2D(lopit2015, fcol = NULL)
```
